Efficient ancestry and mutation simulation with msprime 1.0

### 2021-12-01 paper.tex
Fixup authors

\linenumbers
\title{Efficient ancestry and mutation simulation with msprime 1.0}
% First authors
\author[1,$\star$]{Franz Baumdicker}
\author[2,$\star$]{Gertjan Bisschop}
\author[3,24,$\star$]{Daniel Goldstein}
\author[4,$\star$]{Graham Gower}
\author[5,$\star$]{Aaron P. Ragsdale}
\author[6,$\star$]{Georgia Tsambos}
\author[7,$\star$]{Sha Zhu}

% Middle Authors
\author[8]{Bjarki Eldon}
\author[9]{E. Castedo Ellerman}
\author[10,11]{Jared G. Galloway}
\author[12,13]{Ariella L. Gladstein}
\author[14]{Gregor Gorjanc}
\author[15]{Bing Guo}
\author[7]{Ben Jeffery}
\author[16]{Warren W. Kretzschmar}
% Haven't been able to contact Ivan, so forced to drop for preprint
% \author[17]{Ivan Krukov}
\author[2]{Konrad Lohse}
\author[17]{Michael Matschiner}
\author[18]{Dominic Nelson}
\author[19]{Nathaniel S. Pope}
\author[20]{Consuelo D. Quinto-Cort\'es}
\author[10]{Murillo F. Rodrigues}
\author[21]{Kumar Saunack}
\author[22]{Thibaut Sellinger}
\author[23]{Kevin Thornton}
\author[24]{Hugo van Kemenade}
\author[7,25]{Anthony W. Wohns}
\author[7]{Yan Wong}

@@

\affil[$\star$]{Denotes shared first authorship, listed alphabetically}
\affil[$\dagger$]{Denotes shared senior authorship, listed alphabetically}
\affil[$\ddagger$]{Denotes corresponding author}

% \section*{Contact:} \href{jerome.kelleher@bdi.ox.ac.uk}{jerome.kelleher@bdi.ox.ac.uk}

\maketitle

@@

\textbf{Keywords:} Simulation, Coalescent, Mutations, Ancestral Recombination
Graphs

\section*{Introduction}

>>>>

\title{Efficient ancestry and mutation simulation with msprime 1.0}

% First authors
\author[1,$\star$]{Franz Baumdicker}
\author[2,$\star$]{Gertjan Bisschop}
\author[3,24,$\star$]{Daniel Goldstein}
\author[4,$\star$]{Graham Gower}
\author[5,$\star$]{Aaron P. Ragsdale}
\author[6,$\star$]{Georgia Tsambos}
\author[7,$\star$]{Sha Zhu}

% Middle Authors
\author[8]{Bjarki Eldon}
\author[9]{E. Castedo Ellerman}
\author[10,11]{Jared G. Galloway}
\author[12,13]{Ariella L. Gladstein}
\author[14]{Gregor Gorjanc}
\author[15]{Bing Guo}
\author[7]{Ben Jeffery}
\author[16]{Warren W. Kretzschmar}
\author[2]{Konrad Lohse}
\author[17]{Michael Matschiner}
\author[18]{Dominic Nelson}
\author[19]{Nathaniel S. Pope}
\author[20]{Consuelo D. Quinto-Cort\'es}
\author[10]{Murillo F. Rodrigues}
\author[21]{Kumar Saunack}
\author[22]{Thibaut Sellinger}
\author[23]{Kevin Thornton}
\author[24]{Hugo van Kemenade}
\author[7,25]{Anthony W. Wohns}
\author[7]{Yan Wong}

@@

% % \section*{Contact:} \href{jerome.kelleher@bdi.ox.ac.uk}{jerome.kelleher@bdi.ox.ac.uk}

% \maketitle

\keywords{Simulation, Coalescent, Mutations, Ancestral Recombination Graphs}

\runningtitle{Efficient ancestry and mutation simulation with msprime 1.0}
\runningauthor{Baumdicker \textit{et al.}}

@@

\maketitle
\thispagestyle{firststyle}
\marginmark
\firstpagefootnote

% Use the \equalcontrib command to mark authors with equal
% contributions, using the relevant superscript numbers
% \equalcontrib{1}
% \equalcontrib{2}
\equalcontrib{$\star$} % {Denotes shared first authorship, listed alphabetically}
\equalcontrib{$\dagger$} % {Denotes shared senior authorship, listed alphabetically}
% \equalcontrib{$\ddagger$}{Denotes corresponding author}

\correspondingauthoraffiliation{$\ddagger$}{\url{jerome.kelleher@bdi.ox.ac.uk}}
\vspace{-33pt}% Only used for adjusting extra space in the left column of the first page

\section{Introduction}
